diffusion, websites with 1 pc

### 2023-03-20 src/hex_heatmaps.Rmd
regressions per firm

    stat_binhex(bins=150) + 
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}

@@

    #stat_binhex(bins=150) +
    stat_binhex(aes(fill=log(..count..)), bins=150) +
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='log(Frequency)',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```

>>>>

    stat_binhex(bins=150) + 
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4),
          plot.title = element_text(hjust = 0.5)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}

@@

    #stat_binhex(bins=150) +
    stat_binhex(aes(fill=log(..count..)), bins=150) +
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='log(Frequency)',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4),
          plot.title = element_text(hjust = 0.5)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```

### 2023-03-20 src/level_lisa_la.Rmd
regressions per firm

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}
```

@@

#ggplot map solution.
# mun_merge_new %>% st_as_sf(crs = 27700) %>% #st_transform(4326) %>%
#   ggplot()+
#   geom_sf(aes(fill = as.factor(quadrant)))
# ggsave("test_ggplot.png", path = path)
```

>>>>

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

#ggplot map solution.
# mun_merge_new %>% st_as_sf(crs = 27700) %>% #st_transform(4326) %>%
#   ggplot()+
#   geom_sf(aes(fill = as.factor(quadrant)))
# ggsave("test_ggplot.png", path = path)

@@
